**Selective DNA and Protein Isolation from Marine Macrophyte Surfaces**

### 2021-03-25 submission/manuscript.Rmd

## Summary
Studies of unculturable microbes often combine methods such as 16S rRNA sequencing, metagenomics and metaproteomics. To apply these techniques to the microbial community inhabiting the surfaces of marine macrophytes it is advisable to perform a selective DNA and protein isolation prior to the analysis to avoid biases due to the host material being present in high quantities. Two protocols for DNA and protein isolation were adapted for selective extractions of DNA and proteins from epiphytic communities inhabiting the surfaces of two marine macrophytes, the seagrass *Cymodocea nodosa* and the macroalga *Caulerpa cylindracea*. Protocols showed an almost complete removal of the epiphytic community regardless of the sampling season, station, settlement or host species. The obtained DNA was suitable for metagenomic and 16S rRNA sequencing, while isolated proteins could be identified by mass spectrometry. Low presence of host DNA and proteins in the samples indicated a high specificity of the protocols. The procedures are based on universally available laboratory chemicals making the protocols widely applicable. Taken together, the adapted protocols ensure an almost complete removal of the macrophyte epiphytic community. The procedures are selective for microbes inhabiting macrophyte surfaces and provide DNA and proteins applicable in 16S rRNA sequencing, metagenomics and metaproteomics.

@@

\newpage
## Materials and methods
### Sampling
Leaves of *C. nodosa* were sampled in a *C. nodosa* meadow in the Bay of Saline, northern Adriatic Sea (\ang{45;7;5} N, \ang{13;37;20} E) and in a *C. nodosa* meadow invaded by *C. cylindracea* in the Bay of Funtana, northern Adriatic Sea (\ang{45;10;39} N, \ang{13;35;42} E). Thalli of *C. cylindracea* were sampled in the same *C. nodosa* invaded meadow in the Bay of Funtana and at a locality of only *C. cylindracea* located in the proximity of the invaded meadow. Leaves and thalli for 16S rRNA analysis, metagenomics and metaproteomics were collected in two contrasting seasons, on 4 December 2017 (16S rRNA analysis and metaproteomics), 14 December 2017 (metagenomics) and 18 June 2018 (16S rRNA analysis, metagenomics and metaproteomics). During spring 2018, the *C. nodosa* meadow in the Bay of Saline decayed to an extent that no leaves could be retrieved [@Najdek2020]. In addition, as not enough DNA for both metagenomic and 16S RNA analysis were obtained during the sampling on 4 December 2017, an additional sampling on 14 December 2017 was carried out in the Bay of Funtana. Leaves and thalli were collected by diving and transported to the laboratory in containers placed on ice and filled with seawater from this site. Upon arrival to the laboratory, *C. nodosa* leaves were cut into sections of 1 -- 2 \si{\cm}, while *C. cylindracea* thalli were cut into 5 -- 8 \si{\cm} long sections. Leaves and thalli were washed three times with sterile artificial seawater (ASW) to remove loosely attached microbial cells.

@@

### Illumina 16S rRNA sequencing
An aliquot of isolated DNA was treated with RNase A (final concentration 200 \si{\ug\per\ml}) for 2 \si{\hour} at 37 \si{\degreeCelsius}. The DNA concentration was determined using the Quant-iT PicoGreen dsDNA Assay Kit (Invitrogen, USA) according to the manufacturer’s instructions and diluted to 1 \si{\ng\per\ul}. The V4 region of the 16S rRNA gene was amplified using a two-step PCR procedure. In the first PCR the 515F ($5'$-GTGYCAGCMGCCGCGGTAA-$3'$) and 806R ($5'$-GGACTACNVGGGTWTCTAAT-$3'$) primers from the Earth Microbiome Project (http://press.igsb.anl.gov/earthmicrobiome/protocols-and-standards/16s/) were used to amplify the target region [@Caporaso2012; @Apprill2015; @Parada2016]. These primers contained on their $5'$ end a tagged sequence. Each sample was amplified in four parallel 25 \si{\ul} reactions of which each contained 1 × Q5 Reaction Buffer, 0.2 \si{\milli\Molar} of dNTPmix, 0.7 \si{\mg\per\ml} BSA (Bovine Serum Albumin), 0.2 \si{\micro\Molar} of forward and reverse primers, 0.5 U of Q5 High-Fidelity DNA Polymerase (New England Biolabs, USA) and 5 \si{\ng} of DNA template. Cycling conditions were: initial denaturation at 94 \si{\degreeCelsius} for 3 \si{\minute}, 20 cycles of denaturation at 94 \si{\degreeCelsius} for 45 \si{\s}, annealing at 50 \si{\degreeCelsius} for 60 \si{\s} and elongation at 72 \si{\degreeCelsius} for 90 \si{\s}, finalized by an elongation step at 72 \si{\degreeCelsius} for 10 \si{\minute}. The four parallel reactions volumes were pooled and PCR products were purified using the GeneJET PCR Purification Kit (Thermo Fisher Scientific, USA) according to the manufacturer's instructions and following the protocol that included isopropanol addition for better small DNA fragment yield. The column was eluted in 30 \si{\ul} of deionized water. Purified PCR products were sent for Illumina MiSeq sequencing (2 × 250 bp) at IMGM Laboratories, Martinsried, Germany. Before sequencing at IMGM, the second PCR amplification of the two-step PCR procedure was performed using primers targeting the tagged region incorporated in the first PCR. In addition, these primers contained adapter and sample-specific index sequences. The second PCR was carried out for 8 cycles. Beside samples, a positive and negative control were sequenced. A negative control was comprised of four parallel PCR reactions without DNA template, while for a positive control a mock community composed of evenly mixed DNA material originating from 20 bacterial strains (ATCC MSA-1002, ATCC, USA) was used. Partial 16S rRNA sequences obtained in this study have been deposited in the European Nucleotide Archive (ENA) at EMBL-EBI under accession numbers SAMEA6786270, SAMEA6648792 -- SAMEA6648794, SAMEA6648809 -- SAMEA6648811 and SAMEA6648824.

@@

### Metaproteomics
Isolated proteins were whole trypsin digested using the FASP (filter-aided sample preparation) Protein Digestion Kit (Expedeon, UK) according to the manufacturer's instructions with small modifications [@Wisniewski2009]. Prior to loading the solution onto the column, protein pellets were solubilized in a urea sample buffer included in the kit amended with DTT (final concentration 100 \si{\milli\Molar}) for 45 \si{\minute} at room temperature and centrifuged at 20,000 × g for 2 -- 5 \si{\minute} at room temperature to remove larger particles. The first washing step after protein solution loading was repeated twice. In addition, the centrifugation steps were prolonged if the column was clogged. Trypsin digestion was performed on column filters at 37 \si{\degreeCelsius} overnight for 18 \si{\hour}. The final filtrate containing peptides was acidified with 1 \si{\percent} (final concentration) trifluoroacetic acid (TFA), freezed at \num{-80} \si{\degreeCelsius}, lyophilized and sent to VIME -- Vienna Metabolomics Center (University of Vienna) for metaproteomic analysis. Peptides were re-suspended in 1 \si{\percent} (final concentration) TFA, desalted using the Pierce C18 Tips (Thermo Fisher Scientific, USA) according to the manufacturer's instructions and sequenced on a Q Exactive Hybrid Quadrupole-Orbitrap Mass Spectrometer (Thermo Fisher Scientific, USA). Obtained MS/MS spectra were searched against a protein database composed of combined sequenced metagenomes using SEQUEST-HT engines and validated with Percolator in Proteome Discoverer 2.1 (Thermo Fisher Scientific, USA). The target-decoy approach was used to reduce the probability of false peptide identification. Results whose false discovery rate at the peptide level was < \SI{1}{\percent} were kept. For protein identification a minimum of two peptides and one unique peptide were required. For protein quantification, a chromatographic peak area-based free quantitative method was applied.

### Data processing and visualization
Processing and visualization  of 16S rRNA, metagenomic and metaproteomic data were done using R (version 3.6.0) [@RCoreTeam2019],  package tidyverse (version 1.3.0) [@Wickham2019] and multiple other packages [@Xie2014; @Xie2015; @Xie2019a; @Xie2020; @Allaire2019; @Xie2018; @Zhu2019; @Neuwirth2014; @Bengtsson2020; @Wilke2018]. The detailed analysis procedure including the R Markdown file for this paper are available as a GitHub repository (https://github.com/MicrobesRovinj/Korlevic_SelectiveRemoval_FrontMicrobiol_2021).

@@

# Calculating the number of sequences
number_sequences <- filter(community, taxon=="Archaea" | taxon=="Bacteria") %>%
  select(total) %>%
  sum()

# Calculating the number of chloroplast sequences
number_chloroplast_sequences <- filter(community, taxon=="Chloroplast") %>%
  select(total) %>%
  sum()

@@

# Calculating the minimal and maximal number of sequences
min_max <- filter(community, taxon=="Archaea" | taxon=="Bacteria") %>%
  summarise_at(6:ncol(.), sum) %>%
  summarise(min=min(.), max=max(.))
```

@@

To evaluate whether the obtained DNA is suitable to determine the composition of the microbial community Illumina sequencing of the V4 region of the 16S rRNA was performed. Sequencing yielded a total of `r number_sequences` sequences after quality curation and exclusion of eukaryotic, mitochondrial and no relative sequences. The number of sequences classified as chloroplasts was `r number_chloroplast_sequences`. After excluding these sequences, the total number of retrieved reads was `r number_sequences_without_chloroplast`, ranging from `r min_max$min` to `r min_max$max` sequences per sample (\autoref{supp-nseq_notus}). Even when the highest sequencing effort was applied, the rarefaction curves did not level off which is commonly observed in high-throughput 16S rRNA amplicon sequencing (\autoref{supp-rarefaction}). Sequences clustering at a similarity level of 97 \si{\percent} yielded a total of `r no_otus` different OTUs. Taxonomic classification of reads revealed a macrophyte-associated epiphytic community that mainly composed of *Alphaproteobacteria* (`r filter(plot, taxon=="Alphaproteobacteria")$mean` ± `r filter(plot, taxon=="Alphaproteobacteria")$sd` \si{\percent}), *Bacteroidota* (`r filter(plot, taxon=="Bacteroidota")$mean` ± `r filter(plot, taxon=="Bacteroidota")$sd` \si{\percent}), *Gammaproteobacteria* (`r filter(plot, taxon=="Gammaproteobacteria")$mean` ± `r filter(plot, taxon=="Gammaproteobacteria")$sd` \si{\percent}), *Desulfobacterota* (`r filter(plot, taxon=="Desulfobacterota")$mean` ± `r filter(plot, taxon=="Desulfobacterota")$sd` \si{\percent}), *Cyanobacteria* (`r filter(plot, taxon=="Cyanobacteria")$mean` ± `r filter(plot, taxon=="Cyanobacteria")$sd` \si{\percent}) and *Planctomycetota* (`r filter(plot, taxon=="Planctomycetota")$mean` ± `r filter(plot, taxon=="Planctomycetota")$sd` \si{\percent}) (\autoref{community}).

@@

Successful amplification and sequencing of the V4 region of the 16S rRNA gene proved that the isolated DNA can be used to estimate the microbial epiphytic diversity. Taxonomic groups detected in this step can also be often found in epiphytic communities associated with other macrophytes [@Morrissey2019; @Burke2011a]. A problem often encountered in studies focusing on epiphytic communities is the presence of large proportions of chloroplast 16S rRNA sequences in the pool of amplified molecules, especially if the epiphytic DNA was isolated without prior selection [@Staufenberger2008]. These sequences can derive from host chloroplasts or from eukaryotic epiphytic chloroplast DNA. Although the proportion of obtained chloroplast 16S rRNA sequences in our samples was substantial, they derived almost exclusively from eukaryotic epiphytes. High proportion of chloroplast 16S rRNA sequences in studies applying selective procedures that include direct cellular lysis on host surfaces were observed before [@Michelou2013]. It is possible that chloroplast-specific sequences even in these studies originated from eukaryotic epiphytic cells and not from host chloroplasts. Indeed, it is common during 16S rRNA profiling of pelagic microbial communities to observe high proportions of chloroplast sequences [@Korlevic2016; @Gilbert2009]. In addition, a very low proportion of chloroplast 16S rRNA sequences in samples originating from *C. cylindracea* in comparison to *C. nodosa* could be explained by the presence of three introns in the gene for 16S rRNA in some members of the genus *Caulerpa* that could hamper the amplification process [@Lam2016].

>>>>

## Abstract
Studies of unculturable microbes often combine methods such as 16S rRNA sequencing, metagenomics and metaproteomics. To apply these techniques to the microbial community inhabiting the surfaces of marine macrophytes it is advisable to perform a selective DNA and protein isolation prior to the analysis to avoid biases due to the host material being present in high quantities. Two protocols for DNA and protein isolation were adapted for selective extractions of DNA and proteins from epiphytic communities inhabiting the surfaces of two marine macrophytes, the seagrass *Cymodocea nodosa* and the macroalga *Caulerpa cylindracea*. Protocols showed an almost complete removal of the epiphytic community regardless of the sampling season, station, settlement or host species. The obtained DNA was suitable for metagenomic and 16S rRNA sequencing, while isolated proteins could be identified by mass spectrometry. Low presence of host DNA and proteins in the samples indicated a high specificity of the protocols. The procedures are based on universally available laboratory chemicals making the protocols widely applicable. Taken together, the adapted protocols ensure an almost complete removal of the macrophyte epiphytic community. The procedures are selective for microbes inhabiting macrophyte surfaces and provide DNA and proteins applicable in 16S rRNA sequencing, metagenomics and metaproteomics.

@@

\newpage
## Materials and methods
### Sampling
Leaves of *C. nodosa* were sampled in a *C. nodosa* meadow in the Bay of Saline, northern Adriatic Sea (\ang{45;7;5} N, \ang{13;37;20} E) and in a *C. nodosa* meadow invaded by *C. cylindracea* in the Bay of Funtana, northern Adriatic Sea (\ang{45;10;39} N, \ang{13;35;42} E). Thalli of *C. cylindracea* were sampled in the same *C. nodosa* invaded meadow in the Bay of Funtana and at a locality of only *C. cylindracea* located in the proximity of the invaded meadow. Leaves and thalli for 16S rRNA analysis, metagenomics and metaproteomics were collected in two contrasting seasons, on 4 December 2017 (16S rRNA analysis and metaproteomics), 14 December 2017 (metagenomics) and 18 June 2018 (16S rRNA analysis, metagenomics and metaproteomics). During spring 2018, the *C. nodosa* meadow in the Bay of Saline decayed to an extent that no leaves could be retrieved [@Najdek2020]. In addition, as not enough DNA for both metagenomic and 16S RNA analysis were obtained during the sampling on 4 December 2017, an additional sampling on 14 December 2017 was carried out in the Bay of Funtana. Leaves and thalli were collected by diving and transported to the laboratory in containers placed on ice and filled with seawater from the site. Upon arrival to the laboratory, *C. nodosa* leaves were cut into sections of 1 -- 2 \si{\cm}, while *C. cylindracea* thalli were cut into 5 -- 8 \si{\cm} long sections. Leaves and thalli were washed three times with sterile artificial seawater (ASW) to remove loosely attached microbial cells.

@@

### Illumina 16S rRNA sequencing
An aliquot of isolated DNA was treated with RNase A (final concentration 200 \si{\ug\per\ml}) for 2 \si{\hour} at 37 \si{\degreeCelsius}. The DNA concentration was determined using the Quant-iT PicoGreen dsDNA Assay Kit (Invitrogen, USA) according to the manufacturer’s instructions and diluted to 1 \si{\ng\per\ul}. The V4 region of the 16S rRNA gene was amplified using a two-step PCR procedure. In the first PCR the 515F ($5'$-GTGYCAGCMGCCGCGGTAA-$3'$) and 806R ($5'$-GGACTACNVGGGTWTCTAAT-$3'$) primers from the Earth Microbiome Project (https://earthmicrobiome.org/protocols-and-standards/16s/) were used to amplify the target region [@Caporaso2012; @Apprill2015; @Parada2016]. These primers contained on their $5'$ end a tagged sequence. Each sample was amplified in four parallel 25 \si{\ul} reactions of which each contained 1 × Q5 Reaction Buffer, 0.2 \si{\milli\Molar} dNTPmix, 0.7 \si{\mg\per\ml} BSA (Bovine Serum Albumin), 0.2 \si{\micro\Molar} of forward and reverse primers, 0.5 U of Q5 High-Fidelity DNA Polymerase (New England Biolabs, USA) and 5 \si{\ng} of DNA template. Cycling conditions were: initial denaturation at 94 \si{\degreeCelsius} for 3 \si{\minute}, 20 cycles of denaturation at 94 \si{\degreeCelsius} for 45 \si{\s}, annealing at 50 \si{\degreeCelsius} for 60 \si{\s} and elongation at 72 \si{\degreeCelsius} for 90 \si{\s}, finalized by an elongation step at 72 \si{\degreeCelsius} for 10 \si{\minute}. The four parallel reactions volumes were pooled and PCR products were purified using the GeneJET PCR Purification Kit (Thermo Fisher Scientific, USA) according to the manufacturer's instructions and following the protocol that included isopropanol addition for better small DNA fragment yield. The column was eluted in 30 \si{\ul} of deionized water. Purified PCR products were sent for Illumina MiSeq sequencing (2 × 250 bp) at IMGM Laboratories, Martinsried, Germany. Before sequencing at IMGM, the second PCR amplification of the two-step PCR procedure was performed using primers targeting the tagged region incorporated in the first PCR. In addition, these primers contained adapter and sample-specific index sequences. The second PCR was carried out for 8 cycles. Beside samples, a positive and negative control were sequenced. A negative control was comprised of four parallel PCR reactions without DNA template, while for a positive control a mock community composed of evenly mixed DNA material originating from 20 bacterial strains (ATCC MSA-1002, ATCC, USA) was used. Partial 16S rRNA sequences obtained in this study have been deposited in the European Nucleotide Archive (ENA) at EMBL-EBI under accession numbers SAMEA6786270, SAMEA6648792 -- SAMEA6648794, SAMEA6648809 -- SAMEA6648811 and SAMEA6648824.

@@

### Metaproteomics
Isolated proteins were whole trypsin digested using the FASP (filter-aided sample preparation) Protein Digestion Kit (Expedeon, UK) according to the manufacturer's instructions with small modifications [@Wisniewski2009]. Prior to loading the solution onto the column, protein pellets were solubilized in urea sample buffer included in the kit amended with DTT (final concentration 100 \si{\milli\Molar}) for 45 \si{\minute} at room temperature and centrifuged at 20,000 × g for 2 -- 5 \si{\minute} at room temperature to remove larger particles. The first washing step after protein solution loading was repeated twice. In addition, the centrifugation steps were prolonged if the column was clogged. Trypsin digestion was performed on column filters at 37 \si{\degreeCelsius} overnight for 18 \si{\hour}. The final filtrate containing peptides was acidified with 1 \si{\percent} (final concentration) trifluoroacetic acid (TFA), freezed at \num{-80} \si{\degreeCelsius}, lyophilized and sent to VIME -- Vienna Metabolomics Center (University of Vienna) for metaproteomic analysis. Peptides were re-suspended in 1 \si{\percent} (final concentration) TFA, desalted using the Pierce C18 Tips (Thermo Fisher Scientific, USA) according to the manufacturer's instructions and sequenced on a Q Exactive Hybrid Quadrupole-Orbitrap Mass Spectrometer (Thermo Fisher Scientific, USA). Obtained MS/MS spectra were searched against a protein database composed of combined sequenced metagenomes obtained in this study using SEQUEST-HT engines and validated with Percolator in Proteome Discoverer 2.1 (Thermo Fisher Scientific, USA). The target-decoy approach was used to reduce the probability of false peptide identification. Results whose false discovery rate at the peptide level was < \SI{1}{\percent} were kept. For protein identification a minimum of two peptides and one unique peptide were required. For protein quantification, a chromatographic peak area-based free quantitative method was applied.

### Data processing and visualization
Processing and visualization  of 16S rRNA, metagenomic and metaproteomic data were done using R (version 3.6.0) [@RCoreTeam2019],  package tidyverse (version 1.3.0) [@Wickham2019] and multiple other packages [@Xie2014; @Xie2015; @Xie2019a; @Xie2019b; @Allaire2019; @Xie2018; @Zhu2019; @Neuwirth2014; @Bengtsson2020; @Wilke2018]. The detailed analysis procedure including the R Markdown file for this paper are available as a GitHub repository (https://github.com/MicrobesRovinj/Korlevic_SelectiveRemoval_FrontMicrobiol_2021).

@@

# Calculating the number of sequences
number_sequences <- filter(community, taxon=="Archaea" | taxon=="Bacteria") %>%
  select(`40` : `63`) %>%
  sum()

# Calculating the number of chloroplast sequences
number_chloroplast_sequences <- filter(community, taxon=="Chloroplast") %>%
  select(`40` : `63`) %>%
  sum()

@@

# Calculating the minimal and maximal number of sequences
min_max <- filter(community, taxon=="Archaea" | taxon=="Bacteria" | taxon=="Chloroplast") %>%
  mutate_at(6:ncol(.), list(~case_when(taxon=="Bacteria" ~ . - .[taxon=="Chloroplast"], TRUE ~ .))) %>%
  filter(taxon!="Chloroplast") %>%
  summarise_at(6:ncol(.), sum) %>%
  summarise(min=min(.), max=max(.))
```

@@

To evaluate whether the obtained DNA is suitable to determine the composition of the microbial community Illumina sequencing of the V4 region of the 16S rRNA was performed. Sequencing yielded a total of `r number_sequences` sequences after quality curation and exclusion of eukaryotic, mitochondrial and no relative sequences. The number of sequences classified as chloroplasts was `r number_chloroplast_sequences`. After excluding these sequences, the total number of retrieved reads was `r number_sequences_without_chloroplast`, ranging from `r min_max$min` to `r min_max$max` sequences per sample (\autoref{supp-nseq_notus}). Even when the highest sequencing effort was applied, the rarefaction curves did not level off which is commonly observed in high-throughput 16S rRNA amplicon sequencing (\autoref{supp-rarefaction}). Sequences clustering at a similarity level of 97 \si{\percent} yielded a total of `r no_otus` different OTUs. Taxonomic classification of reads revealed a macrophyte-associated epiphytic community mainly composed of *Alphaproteobacteria* (`r filter(plot, taxon=="Alphaproteobacteria")$mean` ± `r filter(plot, taxon=="Alphaproteobacteria")$sd` \si{\percent}), *Bacteroidota* (`r filter(plot, taxon=="Bacteroidota")$mean` ± `r filter(plot, taxon=="Bacteroidota")$sd` \si{\percent}), *Gammaproteobacteria* (`r filter(plot, taxon=="Gammaproteobacteria")$mean` ± `r filter(plot, taxon=="Gammaproteobacteria")$sd` \si{\percent}), *Desulfobacterota* (`r filter(plot, taxon=="Desulfobacterota")$mean` ± `r filter(plot, taxon=="Desulfobacterota")$sd` \si{\percent}), *Cyanobacteria* (`r filter(plot, taxon=="Cyanobacteria")$mean` ± `r filter(plot, taxon=="Cyanobacteria")$sd` \si{\percent}) and *Planctomycetota* (`r filter(plot, taxon=="Planctomycetota")$mean` ± `r filter(plot, taxon=="Planctomycetota")$sd` \si{\percent}) (\autoref{community}).

@@

Successful amplification and sequencing of the V4 region of the 16S rRNA gene proved that the isolated DNA can be used to estimate the microbial epiphytic diversity. Taxonomic groups detected in this step can also be often found in epiphytic communities associated with other macrophytes [@Morrissey2019; @Burke2011a]. A problem often encountered in studies focusing on epiphytic communities is the presence of large proportions of chloroplast 16S rRNA sequences in the pool of amplified molecules, especially if the epiphytic DNA was isolated without prior selection [@Staufenberger2008]. These sequences can derive from host chloroplasts or from eukaryotic epiphytic chloroplast DNA. Although the proportion of obtained chloroplast 16S rRNA sequences in our samples was substantial, they derived almost exclusively from eukaryotic epiphytes. High proportion of chloroplast 16S rRNA sequences in studies applying selective procedures that include direct cellular lysis on host surfaces were observed before [@Michelou2013]. It is possible that chloroplast-specific sequences even in these studies originated from eukaryotic epiphytic cells and not from host chloroplasts. Indeed, it is common during 16S rRNA profiling of pelagic microbial communities to observe high proportions of chloroplast sequences [@Korlevic2016; @Gilbert2009]. On of the solutions to further reduce chloroplast 16S rRNA sequence contamination is to use primers that minimise the amplification of these reads if the sequencing and study design allow it [@Hanshew2013]. In addition, a very low proportion of chloroplast 16S rRNA sequences in samples originating from *C. cylindracea* in comparison to *C. nodosa* could be explained by the presence of three introns in the gene for 16S rRNA in some members of the genus *Caulerpa* that could hamper the amplification process [@Lam2016].
